Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2024-06-13 mop/draft.tex
update from overleaf

\begin{figure}[ht]
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, auto,
>=Latex,every node/.append style={align=center}, 
int/.style={draw, minimum size=1.6cm}]
  \node [int] (H) at (0,0) {$H$};
\node [int] (S) [right=of H] {$S$};
\node [int] (I) [right=of S] {$I$};
\node (Mcoord) [right=of I, coordinate] {Mcoord};
\node [int] (R1) [right=of Mcoord] {$R_1$};
\node [int] (R2) [right=of R1] {$R_2$};
\node [int] (R3) [right=of R2] {$R_3$};
\node [circle, draw] (M) [above=of Mcoord] {$M$};
\node (deathsS) [above=of S, coordinate] {deathsS};
\node (deathsI) [above=of I, coordinate] {deathsS};
\node (deathsR1) [above=of R1, coordinate] {deathsR1};
\node (deathsR2) [above=of R2, coordinate] {deathsR2};
\node (deathsR3) [above=of R3, coordinate] {deathsR3};
\node (belowR3) [below=of R3, coordinate] {belowR3};
\node (belowS) [below=of S, coordinate] {belowS};
\path[->]
    (H) edge node {$dH$} (S)
    (S) edge node {$\lambda(t)$}  (I)
    (I) edge node {$\gamma$}  (R1)
    (R1) edge node {$k\epsilon$}  (R2)
    (R2) edge node {$k\epsilon$}  (R3)
    (R3) edge node {} (belowR3) 
    (belowR3) edge node {$k\epsilon$} (belowS) 
    (belowS) edge node {} (S)
    (I) edge node {$m$}  (M)
    (S) edge node {$\delta$}  (deathsS)
    (I) edge node {$\delta$}  (deathsI)
    (R1) edge node {$\delta$}  (deathsR1)
    (R2) edge node {$\delta$}  (deathsR2)
    (R3) edge node {$\delta$}  (deathsR3);
\end{tikzpicture}
\caption{Illustration of SIR model from \cite{king08}.}
\label{fig:sir}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, auto,
>=Latex,every node/.append style={align=center}, 
int/.style={draw, minimum size=1.6cm}]
  \node [int] (H) at (0,0) {$P$};
\node [int] (S) [right=of H] {$S$};
\node [int] (I) [right=of S] {$I$};
\node (Mcoord) [right=of I, coordinate] {Mcoord};
\node [int] (R1) [right=of Mcoord] {$R_1$};
\node [int] (R2) [right=of R1] {$R_2$};
\node [int] (R3) [right=of R2] {$R_3$};
\node [circle, draw] (M) [above=of Mcoord] {$M$};
\node (deathsS) [above=of S, coordinate] {deathsS};
\node (deathsI) [above=of I, coordinate] {deathsS};
\node (deathsR1) [above=of R1, coordinate] {deathsR1};
\node (deathsR2) [above=of R2, coordinate] {deathsR2};
\node (deathsR3) [above=of R3, coordinate] {deathsR3};
\node (belowR3) [below=of R3, coordinate] {belowR3};
\node (belowS) [below=of S, coordinate] {belowS};
\path[->]
    (H) edge node {$dP$} (S)
    (S) edge node {$\lambda(t)$}  (I)
    (I) edge node {$\gamma$}  (R1)
    (R1) edge node {$k\epsilon$}  (R2)
    (R2) edge node {$k\epsilon$}  (R3)
    (R3) edge node {} (belowR3) 
    (belowR3) edge node {$k\epsilon$} (belowS) 
    (belowS) edge node {} (S)
    (I) edge node {$m$}  (M)
    (S) edge node {$\delta$}  (deathsS)
    (I) edge node {$\delta$}  (deathsI)
    (R1) edge node {$\delta$}  (deathsR1)
    (R2) edge node {$\delta$}  (deathsR2)
    (R3) edge node {$\delta$}  (deathsR3);
\end{tikzpicture}
\caption{Illustration of SIR model from \cite{king08}.}
\label{fig:sir}
\end{figure}
